---
title: "CSA: Health impact and cost-effectiveness of community-supported agriculture"
author: "Sanjay Basu"
date: "07/23/2019"
output: html_document
---

```{r setup, include=FALSE}

install.packages('nhanesA', repos = "https://cran.rstudio.com")
install.packages('stringr', repos = "https://cran.rstudio.com")
install.packages('data.table', repos = "https://cran.rstudio.com")
install.packages('knitr', repos = "https://cran.rstudio.com")
options(repos="https://cran.rstudio.com" )
knitr::opts_chunk$set(echo = TRUE)
setwd("~/Box/Analytics Team/Research/Research Projects/CSA")
```

## Health impact and cost-effectiveness of community-supported agriculture

A a randomized clinical trial (NCT03231592) has revealed that participation in a community supported agriculture (CSA) intervention resulted in clinically meaningful improvements in diet quality. We sought to identify the population-level impact of broadened national CSA availability on cardiometabolic disease incidence and mortality, and assess the intervention's cost-effectiveness.

Sanjay Basu*, Seth Berkowitz

*sanjay_basu@hms.harvard.edu



# NHANES pop

- use NHANES Population
- set eligibles to <200% FPL or Medicaid
- get variables for ASCVD inc, DM inc, DM microvasc complications, and all-cause mort [PCEs and RECODE]

```{r nhanes}
library(nhanesA)
demo <- nhanes('DEMO_H')
bmx <- nhanes('BMX_H')
tchol <- nhanes('TCHOL_H')
hdl <- nhanes('HDL_H')
bpq <- nhanes('BPQ_H')
ghb <- nhanes('GHB_H')
diq <- nhanes('DIQ_H')
biopro <- nhanes('BIOPRO_H')
albcr <- nhanes('ALB_CR_H')
bpx <- nhanes('BPX_H')
diet <- nhanes('DR1IFF_H')
rxq <- nhanes('RXQ_RX_H')
smq <- nhanes('SMQ_H')
mcq <- nhanes('MCQ_H')
occ <- nhanes('OCQ_H')
glu <- nhanes('GLU_H')
hic <- nhanes('HIQ_H')

demo2 <- nhanes('DEMO_I')
bmx2 <- nhanes('BMX_I')
tchol2 <- nhanes('TCHOL_I')
hdl2 <- nhanes('HDL_I')
bpq2 <- nhanes('BPQ_I')
ghb2 <- nhanes('GHB_I')
diq2 <- nhanes('DIQ_I')
biopro2 <- nhanes('BIOPRO_I')
albcr2 <- nhanes('ALB_CR_I')
bpx2 <- nhanes('BPX_I')
diet2 <- nhanes('DR1IFF_I')
rxq2 <- nhanes('RXQ_RX_I')
smq2 <- nhanes('SMQ_I')
mcq2 <- nhanes('MCQ_I')
occ2 <- nhanes('OCQ_I')
glu2 <- nhanes('GLU_I')
hic2 <- nhanes('HIQ_I')

demo <- nhanesTranslate('DEMO_H', 
                        colnames = c('RIAGENDR','RIDRETH1'), 
                        data=demo)
demo2 <- nhanesTranslate('DEMO_I', 
                        colnames = c('RIAGENDR','RIDRETH1'), 
                        data=demo2)



merged = merge(demo, bmx)
merged = merge(merged, tchol)
merged = merge(merged, hdl)
merged = merge(merged, bpq)
merged = merge(merged, ghb)
merged = merge(merged, diq)
merged = merge(merged, biopro)
merged = merge(merged, albcr)
merged = merge(merged, bpx)
merged = merge(merged, diet) 
merged = merge(merged, rxq)
merged = merge(merged, smq)
merged = merge(merged, mcq)
merged = merge(merged, occ)
merged = merge(merged, glu)
merged = merge(merged, hic)

merged2 = merge(demo2, bmx2)
merged2 = merge(merged2, tchol2)
merged2 = merge(merged2, hdl2)
merged2 = merge(merged2, bpq2)
merged2 = merge(merged2, ghb2)
merged2 = merge(merged2, diq2)
merged2 = merge(merged2, biopro2)
merged2 = merge(merged2, albcr2)
merged2 = merge(merged2, bpx2)
merged2 = merge(merged2, diet2) 
merged2 = merge(merged2, rxq2)
merged2 = merge(merged2, smq2)
merged2 = merge(merged2, mcq2)
merged2 = merge(merged2, occ2)
merged2 = merge(merged2, glu2)
merged2 = merge(merged2, hic2)

# https://www.r-bloggers.com/combining-dataframes-when-the-columns-dont-match/
rbind.match.columns <- function(input1, input2) {
    n.input1 <- ncol(input1)
    n.input2 <- ncol(input2)
 
    if (n.input2 < n.input1) {
        TF.names <- which(names(input2) %in% names(input1))
        column.names <- names(input2[, TF.names])
    } else {
        TF.names <- which(names(input1) %in% names(input2))
        column.names <- names(input1[, TF.names])
    }
 
    return(rbind(input1[, column.names], input2[, column.names]))
}
 
mergedt = rbind.match.columns(merged, merged2)

save(mergedt, file="merged.RData")
