---
title: "CSA: Health impact and cost-effectiveness of community-supported agriculture"
author: "Sanjay Basu"
date: "2/15/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
setwd("~/Documents/Epi/Research/SDH/CSA")
```

## Health impact and cost-effectiveness of community-supported agriculture


```{r packages}
install.packages('nhanesA')
install.packages('stringr')
install.packages('data.table')

```

## NHANES pop

- use NHANES Population
- set eligibles to <200% FPL or Medicaid
- get variables for ASCVD inc, DM inc, DM microvasc complications, and all-cause mort [PCEs and RECODE]

```{r nhanes}
library(nhanesA)
demo <- nhanes('DEMO_H')
bmx <- nhanes('BMX_H')
tchol <- nhanes('TCHOL_H')
hdl <- nhanes('HDL_H')
bpq <- nhanes('BPQ_H')
ghb <- nhanes('GHB_H')
diq <- nhanes('DIQ_H')
biopro <- nhanes('BIOPRO_H')
albcr <- nhanes('ALB_CR_H')
bpx <- nhanes('BPX_H')
diet <- nhanes('DR1IFF_H')
rxq <- nhanes('RXQ_RX_H')
smq <- nhanes('SMQ_H')
mcq <- nhanes('MCQ_H')
occ <- nhanes('OCQ_H')
glu <- nhanes('GLU_H')
hic <- nhanes('HIQ_H')

demo2 <- nhanes('DEMO_I')
bmx2 <- nhanes('BMX_I')
tchol2 <- nhanes('TCHOL_I')
hdl2 <- nhanes('HDL_I')
bpq2 <- nhanes('BPQ_I')
ghb2 <- nhanes('GHB_I')
diq2 <- nhanes('DIQ_I')
biopro2 <- nhanes('BIOPRO_I')
albcr2 <- nhanes('ALB_CR_I')
bpx2 <- nhanes('BPX_I')
diet2 <- nhanes('DR1IFF_I')
rxq2 <- nhanes('RXQ_RX_I')
smq2 <- nhanes('SMQ_I')
mcq2 <- nhanes('MCQ_I')
occ2 <- nhanes('OCQ_I')
glu2 <- nhanes('GLU_I')
hic2 <- nhanes('HIQ_I')

demo <- nhanesTranslate('DEMO_H', 
                        colnames = c('RIAGENDR','RIDRETH1'), 
                        data=demo)
demo2 <- nhanesTranslate('DEMO_I', 
                        colnames = c('RIAGENDR','RIDRETH1'), 
                        data=demo2)



merged = merge(demo, bmx)
merged = merge(merged, tchol)
merged = merge(merged, hdl)
merged = merge(merged, bpq)
merged = merge(merged, ghb)
merged = merge(merged, diq)
merged = merge(merged, biopro)
merged = merge(merged, albcr)
merged = merge(merged, bpx)
merged = merge(merged, diet) 
merged = merge(merged, rxq)
merged = merge(merged, smq)
merged = merge(merged, mcq)
merged = merge(merged, occ)
merged = merge(merged, glu)
merged = merge(merged, hic)

merged2 = merge(demo2, bmx2)
merged2 = merge(merged2, tchol2)
merged2 = merge(merged2, hdl2)
merged2 = merge(merged2, bpq2)
merged2 = merge(merged2, ghb2)
merged2 = merge(merged2, diq2)
merged2 = merge(merged2, biopro2)
merged2 = merge(merged2, albcr2)
merged2 = merge(merged2, bpx2)
merged2 = merge(merged2, diet2) 
merged2 = merge(merged2, rxq2)
merged2 = merge(merged2, smq2)
merged2 = merge(merged2, mcq2)
merged2 = merge(merged2, occ2)
merged2 = merge(merged2, glu2)
merged2 = merge(merged2, hic2)

# https://www.r-bloggers.com/combining-dataframes-when-the-columns-dont-match/
rbind.match.columns <- function(input1, input2) {
    n.input1 <- ncol(input1)
    n.input2 <- ncol(input2)
 
    if (n.input2 < n.input1) {
        TF.names <- which(names(input2) %in% names(input1))
        column.names <- names(input2[, TF.names])
    } else {
        TF.names <- which(names(input1) %in% names(input2))
        column.names <- names(input1[, TF.names])
    }
 
    return(rbind(input1[, column.names], input2[, column.names]))
}
 
mergedt = rbind.match.columns(merged, merged2)

save(mergedt, file="merged.RData")
mergedt$eligible = ((mergedt$INDFMPIR<2) | (mergedt$HIQ031D==17))
table(mergedt$eligible)
mergedsub = mergedt[which(mergedt$eligible==1),]

age = mergedsub$RIDAGEYR
female = (mergedsub$RIAGENDR=="Female")
black = (mergedsub$RIDRETH1=="Non-Hispanic Black")
black[is.na(black)]=0
hisp = (mergedsub$RIDRETH1=="Other Hispanic")
hisp[is.na(hisp)]=0
bmi = mergedsub$BMXBMI
bmi[is.na(bmi)]=mean(na.omit(bmi))
totchol = mergedsub$LBXTC
totchol[is.na(totchol)]=mean(na.omit(totchol))
hdlc = mergedsub$LBDHDD
hdlc[is.na(hdlc)]=mean(na.omit(hdlc))
dm = (mergedsub$DIQ010==1) | 
  (mergedsub$LBXGH>=6.5) | 
  (mergedsub$LBXGLU>=126)
dm[is.na(dm)]=0
sercreat = mergedsub$LBXSCR
sercreat[is.na(sercreat)]=mean(na.omit(sercreat))
uralbcreat =  mergedsub$URDACT
uralbcreat[is.na(uralbcreat)]=mean(na.omit(uralbcreat))
sysbp = mergedsub$BPXSY1
sysbp[is.na(sysbp)]=mean(na.omit(sysbp))
rxbp = (mergedsub$BPQ040A==1)
rxbp[is.na(rxbp)]=0
cvdhist = (mergedsub$MCQ160F==1)|(mergedsub$MCQ160F==1)
cvdhist[is.na(cvdhist)]=0
hgba1c = mergedsub$LBXGH
hgba1c[is.na(hgba1c)]=mean(na.omit(hgba1c))
cursmoke = (mergedsub$SMQ040==1 | mergedsub$SMQ040==2)
cursmoke[is.na(cursmoke)]=0

library(stringr)
statin = grepl("STATIN",mergedsub$RXDDRUG)
statin[is.na(statin)]=0
oralrx = grepl("METFORMIN",mergedsub$RXDDRUG)|grepl("GLIPIZIDE",mergedsub$RXDDRUG)
oralrx[is.na(oralrx)]=0
anticoag = grepl("WARFARIN",mergedsub$RXDDRUG)
anticoag[is.na(anticoag)]=0
```

## Calculate baseline risk scores, 10 year and lifetime horizons

1. Yadlowsky S, Hayward RA, Sussman JB, McClelland RL, Min Y, Basu S. Clinical Implications of Revised Pooled Cohort Equations for Estimating Atherosclerotic Cardiovascular Disease Risk. Ann Intern Med. ;169:20–29. doi: 10.7326/M17-3011

2. Basu S, Sussman JB, Berkowitz SA, Hayward RA, Yudkin JS. Development and validation of Risk Equations for Complications Of type 2 Diabetes (RECODe) using individual participant data from randomised trials. Lancet Diabetes Endocrinol. 2017;5(10):788-798.

3. Sanjay Basu, Jeremy B. Sussman, Seth A. Berkowitz, Rodney A. Hayward, Alain G. Bertoni, Adolfo Correa, Stanford Mwasongwe, John S. Yudkin. Validation of Risk Equations for Complications of Type 2 Diabetes (RECODe) Using Individual Participant Data From Diverse Longitudinal Cohorts in the U.S. Diabetes Care Mar 2018, 41 (3) 586-595; DOI: 10.2337/dc17-2002




```{r baseline risk scores, 10 year}

# ASCVD
ascvd_10   = ( 1.0*female / (1.0 + exp( - (
  -12.823110 +
    0.106501 * as.numeric(age) +
    0.432440 * as.numeric(black) +
    0.000056 * (as.numeric(sysbp) ^ 2) +
    0.017666 * as.numeric(sysbp) +
    0.731678 * as.numeric(rxbp) +
    0.943970 * as.numeric(dm) +
    1.009790 * as.numeric(cursmoke) +
    0.151318 * (as.numeric(totchol) / as.numeric(hdlc)) +
    -0.008580 * as.numeric(age) * as.numeric(black) +
    -0.003647 * as.numeric(sysbp) * as.numeric(rxbp) +
    0.006208 * as.numeric(sysbp) * as.numeric(black) +
    0.152968 * as.numeric(black) * as.numeric(rxbp) +
    -0.000153 * as.numeric(age) * as.numeric(sysbp) +
    0.115232 * as.numeric(black) * as.numeric(dm) +
    -0.092231 * as.numeric(black) * as.numeric(cursmoke) +
    0.070498 * as.numeric(black) * (as.numeric(totchol) / as.numeric(hdlc)) +
    -0.000173 * as.numeric(black)  * as.numeric(sysbp) * as.numeric(rxbp) +
    -0.000094 * as.numeric(age) * as.numeric(sysbp) * as.numeric(black)))))+
  (1.0*(1-female) / (1.0 + exp( - (
  -11.679980 +
    0.064200 * as.numeric(age) +
    0.482835 * as.numeric(black) +
    -0.000061 * (as.numeric(sysbp) ^ 2) +
    0.038950 * as.numeric(sysbp) +
    2.055533 * as.numeric(rxbp) +
    0.842209 * as.numeric(dm) +
    0.895589 * as.numeric(cursmoke) +
    0.193307 * (as.numeric(totchol) / as.numeric(hdlc)) +
    -0.014207 * as.numeric(sysbp) * as.numeric(rxbp) +
    0.011609 * as.numeric(sysbp) * as.numeric(black) +
    -0.119460 * as.numeric(rxbp) * as.numeric(black) +
    0.000025 * as.numeric(age) * as.numeric(sysbp) +
    -0.077214 * as.numeric(black) * as.numeric(dm) +
    -0.226771 * as.numeric(black) * as.numeric(cursmoke) +
    -0.117749 * (as.numeric(totchol) / as.numeric(hdlc)) * as.numeric(black) +
    0.004190 * as.numeric(black) * as.numeric(rxbp) * as.numeric(sysbp) +
    -0.000199 * as.numeric(black) * as.numeric(age) * as.numeric(sysbp)))))

      
# DM incidence
# https://www.cdc.gov/diabetes/data/statistics-report/incidence-diabetes.html
dminc_10 = (mean(c(.031,.068))*(age<45)+
  mean(c(.109,.068))*(age>=45 & age<65)+
  mean(c(.094,.068))*(age>=65))*100/1000*10


# DM neph
nbetax = (-1.938e-02*age+
           -1.129e-02*female+
           -8.812e-02*black+
           2.338e-01*hisp+
           1.483e-01*cursmoke+
           3.027e-03*sysbp+
           -7.952e-02*rxbp+
           -1.256e-01*oralrx+
           3.199e-02*anticoag+
           -2.164e-02*cvdhist+
           1.369e-01*hgba1c+
           -1.112e-03*totchol+
           6.289e-03*hdlc+
           8.609e-01*sercreat+
           3.615e-04*uralbcreat)
esrdrisk_10 = 1-.973^exp(nbetax-mean(nbetax,na.rm=T))

# DM retin

rbetax = (2.285e-02*age+
           2.264e-01*female+
           -1.677e-01*black+
           8.243e-03*sysbp+
           6.393e-02*rxbp+
           -2.349e-01*oralrx+
           1.127e-01*cvdhist+
           1.449e-01*hgba1c+
           -1.676e-04*totchol+
           5.447e-03*hdlc+
           6.947e-01*sercreat+
           1.992e-04*uralbcreat)
retinrisk_10 = 1 - .92^exp(rbetax-mean(rbetax,na.rm=T))


# DM neuro
ebetax = (0.0302237*age+
           -0.1868000*female+
            -0.0944841*black+
           0.0045609*sysbp+
           0.1819157*rxbp+
           -0.2574724*oralrx+
           0.2667152*cvdhist+
           0.1886579*hgba1c+
           0.0021850*totchol+
           -0.0053887*hdlc+
           0.6044183*sercreat)
neurorisk_10 = 1 - .87^exp(ebetax-mean(ebetax,na.rm=T))



# All cause mort
abetax = (6.703e-02*age+
           -1.529e-01*female+
            -2.393e-02*black+
           5.399e-01*cursmoke+
           -2.988e-03*sysbp+
           8.776e-02*rxbp+
           -2.681e-01*statin+
           4.036e-01*anticoag+
           -0.2574724*oralrx+
           5.888e-01*cvdhist+
           1.659e-01*hgba1c+
           -9.478e-04*totchol+
           -4.378e-03*hdlc+
           3.597e-01*sercreat+
           3.889e-04*uralbcreat)
mortrisk_10 = 1 - .93^exp(abetax-mean(abetax,na.rm=T))
```

```{r baseline risk scores, lifetime}
# https://www.cdc.gov/nchs/data/nvsr/nvsr66/nvsr66_04.pdf
lifeexp = (female==0)*(black==0)*(hisp==0)*( # NH WM (non-Hispanic White Male)
62.1*(age<20)+
57.3*(age>=20 & age<25)+
52.6*(age>=25 & age<30)+
47.9*(age>=30 & age<35)+
43.3*(age>=35 & age<40)+
38.7*(age>=40 & age<45)+
34.2*(age>=45 & age<50)+
29.8*(age>=50 & age<55)+
25.7*(age>=55 & age<60)+
21.7*(age>=60 & age<65)+
18*(age>=65 & age<70)+
14.4*(age>=70 & age<75)+
11.2*(age>=75 & age<80)+
8.3*(age>=80)
)+
  (female==1)*(black==0)*(hisp==0)*( # NH WF
66.7*(age<20)+
61.8*(age>=20 & age<25)+
56.9*(age>=25 & age<30)+
52.1*(age>=30 & age<35)+
47.3*(age>=35 & age<40)+
42.5*(age>=40 & age<45)+
37.9*(age>=45 & age<50)+
33.3*(age>=50 & age<55)+
28.9*(age>=55 & age<60)+
24.7*(age>=60 & age<65)+
20.5*(age>=65 & age<70)+
16.6*(age>=70 & age<75)+
13*(age>=75 & age<80)+
9.7*(age>=80)
  )+
  (female==0)*(black==1)*(hisp==0)*( # NH BM
58.3*(age<20)+
53.6*(age>=20 & age<25)+
49*(age>=25 & age<30)+
44.5*(age>=30 & age<35)+
40*(age>=35 & age<40)+
35.6*(age>=40 & age<45)+
31.2*(age>=45 & age<50)+
27*(age>=50 & age<55)+
23*(age>=55 & age<60)+
19.4*(age>=60 & age<65)+
16.3*(age>=65 & age<70)+
13.2*(age>=70 & age<75)+
10.5*(age>=75 & age<80)+
8.1*(age>=80)  
)+
  (female==1)*(black==1)*(hisp==0)*( # NH BF
64.2*(age<20)+
59.3*(age>=20 & age<25)+
54.5*(age>=25 & age<30)+
49.7*(age>=30 & age<35)+
44.9*(age>=35 & age<40)+
40.3*(age>=40 & age<45)+
35.7*(age>=45 & age<50)+
31.3*(age>=50 & age<55)+
27.2*(age>=55 & age<60)+
23.3*(age>=60 & age<65)+
19.5*(age>=65 & age<70)+
16*(age>=70 & age<75)+
12.7*(age>=75 & age<80)+
9.8*(age>=80)      
  )+
  (female==0)*(black==0)*(hisp==1)*( # HM
65*(age<20)+
60.1*(age>=20 & age<25)+
55.4*(age>=25 & age<30)+
50.7*(age>=30 & age<35)+
45.9*(age>=35 & age<40)+
41.2*(age>=40 & age<45)+
36.6*(age>=45 & age<50)+
32.1*(age>=50 & age<55)+
27.7*(age>=55 & age<60)+
23.6*(age>=60 & age<65)+
19.7*(age>=65 & age<70)+
16*(age>=70 & age<75)+
12.6*(age>=75 & age<80)+
9.5*(age>=80)    
)+
  (female==1)*(black==0)*(hisp==1)*( # HF
70*(age<20)+
65*(age>=20 & age<25)+
60.2*(age>=25 & age<30)+
55.3*(age>=30 & age<35)+
50.4*(age>=35 & age<40)+
45.5*(age>=40 & age<45)+
40.7*(age>=45 & age<50)+
36.1*(age>=50 & age<55)+
31.5*(age>=55 & age<60)+
27*(age>=60 & age<65)+
22.8*(age>=65 & age<70)+
18.7*(age>=70 & age<75)+
14.8*(age>=75 & age<80)+
11.2*(age>=80)       
  )

ascvd_rate = -log(1-ascvd_10)/10
ascvd_life = 1-exp(-ascvd_rate*lifeexp)

dminc_rate = -log(1-dminc_10)/10
dminc_life = 1-exp(-dminc_rate*lifeexp)

esrdrisk_rate = -log(1-esrdrisk_10)/10
esrdrisk_life = 1-exp(-esrdrisk_rate*lifeexp)

retinrisk_rate = -log(1-retinrisk_10)/10
retinrisk_life = 1-exp(-retinrisk_rate*lifeexp)

neurorisk_rate = -log(1-neurorisk_10)/10
neurorisk_life = 1-exp(-neurorisk_rate*lifeexp)

mortrisk_rate = -log(1-mortrisk_10)/10
mortrisk_life = 1-exp(-mortrisk_rate*lifeexp)

```


## Calculate change in incidence and mortality risk due to change in HEI


Process:  Converted raw data from Just Roots trial to % change in diet quality and averaged across 3 diet quality scores (HEI 2010, AHEI 2010, DASH Diet Score). Then related change in diet quality to change in outcome using randomized trials (when available) or prospective cohort studies that examined change in diet quality (as opposed to associations with baseline diet quality) to estimate effects. All effects had to be in at least 1 of the above 3 diet quality indices. I converted effect estimate to being for either a 10% or 20% change in diet quality, as specified above, based on information in cited articles. If effect estimates presented for more than 1 diet quality index, I averaged across available indices.  

Treatment effect 1:  13% (95%CI 9% to 17%) increase in diet quality as measured by HEI, AHEI, or DASH Diet index

Treatment effect 2: 7% (95%CI 3% to 11%) increase in diet quality as measured by HEI, AHEI, or DASH Diet index

Hazard Ratio for CVD Incidence for 20% change in diet quality: 0.91 (0.84–0.97)2

Hazard ratio for incident diabetes for 10% change in diet quality4: 0.84 (95%CI 0.78–0.90)

Change in HbA1c per 10% change in diet quality (in individuals with diabetes):3 -0.32 (95% CI -0.41 to -0.23%) (one time drop, assumed sustained)

Hazard Ratio for all-cause mortality for 20% change in diet quality1: 0.83 (95%CI: 0.78 to 0.88)


1. 	Sotos-Prieto M, Bhupathiraju SN, Mattei J, et al. Association of Changes in Diet Quality with Total and Cause-Specific Mortality. N Engl J Med. 2017;377(2):143-153. doi:10.1056/NEJMoa1613502
2. 	Sotos-Prieto Mercedes, Bhupathiraju Shilpa N., Mattei Josiemer, et al. Changes in Diet Quality Scores and Risk of Cardiovascular Disease Among US Men and Women. Circulation. 2015;132(23):2212-2219. doi:10.1161/CIRCULATIONAHA.115.017158
3. 	Schwingshackl L, Chaimani A, Hoffmann G, Schwedhelm C, Boeing H. A network meta-analysis on the comparative efficacy of different dietary approaches on glycaemic control in patients with type 2 diabetes mellitus. Eur J Epidemiol. 2018;33(2):157-170. doi:10.1007/s10654-017-0352-x
4. 	Ley SH, Pan A, Li Y, et al. Changes in Overall Diet Quality and Subsequent Type 2 Diabetes Risk: Three U.S. Prospective Cohorts. Diabetes Care. September 2016:dc160574. doi:10.2337/dc16-0574


```{r change in incidence and mortality due to change in HEI}


# input pars
iters=length(ascvd_10)
set.seed(1)
hr_ascvd = rnorm(iters, 1-0.91, (0.91-0.84)/1.96)/.2
hr_ascvd[hr_ascvd<0]=0
set.seed(2)
hr_dminc = rnorm(iters, 1-0.84, (0.84-0.78)/1.96)/.1
hr_dminc[hr_dminc<0]=0
set.seed(3)
delta_a1c = rnorm(iters, 0.32, (0.32-0.23)/1.96)/.1
delta_a1c[delta_a1c<0]=0
# appendix to doi:10.1001/jamainternmed.2014.2894
# change in microvasc per 1% change in a1c
hr_renal = 1-1/1.14/.9
hr_neuro = 1-1/1.19/.9
hr_retin = 1-1/1.29/.9
set.seed(4)
hr_allmort = rnorm(iters, 1-0.83, (0.83-0.78)/1.96)/.2
hr_allmort[hr_allmort<0]=0

# rx effect 1
set.seed(5)
rx1_heidelta = rnorm(iters,0.13,(.13-.09)/1.96)
rx1_heidelta[rx1_heidelta<0]=0
rx1_ascvd_10 = (1-rx1_heidelta*hr_ascvd)*ascvd_10
rx1_ascvd_life = (1-rx1_heidelta*hr_ascvd)*ascvd_life
rx1_ascvd_life[rx1_ascvd_life>1]=1
rx1_dminc_10 = (1-rx1_heidelta*hr_dminc)*dminc_10
rx1_dminc_life = (1-rx1_heidelta*hr_dminc)*dminc_life
rx1_esrdrisk_10 = (1-rx1_heidelta*delta_a1c*hr_renal)*esrdrisk_10
rx1_esrdrisk_life = (1-rx1_heidelta*delta_a1c*hr_renal)*esrdrisk_life
rx1_retinrisk_10 = (1-rx1_heidelta*delta_a1c*hr_retin)*retinrisk_10
rx1_retinrisk_life = (1-rx1_heidelta*delta_a1c*hr_retin)*retinrisk_life
rx1_neurorisk_10 = (1-rx1_heidelta*delta_a1c*hr_neuro)*neurorisk_10
rx1_neurorisk_life = (1-rx1_heidelta*delta_a1c*hr_neuro)* neurorisk_life
rx1_allmort_10 = (1-rx1_heidelta*hr_allmort)*mortrisk_10
rx1_allmort_life = (1-rx1_heidelta*hr_allmort)*mortrisk_life

# rx effect 2
set.seed(6)
rx2_heidelta = rnorm(iters,0.07,(.07-.03)/1.96) 
rx2_heidelta[rx2_heidelta<0]=0
rx2_ascvd_10 = (1-rx2_heidelta*hr_ascvd)*ascvd_10
rx2_ascvd_life = (1-rx2_heidelta*hr_ascvd)*ascvd_life
rx2_ascvd_life[rx2_ascvd_life>1]=1
rx2_dminc_10 = (1-rx2_heidelta*hr_dminc)*dminc_10
rx2_dminc_life = (1-rx2_heidelta*hr_dminc)*dminc_life
rx2_esrdrisk_10 = (1-rx2_heidelta*delta_a1c*hr_renal)*esrdrisk_10
rx2_esrdrisk_life = (1-rx2_heidelta*delta_a1c*hr_renal)*esrdrisk_life
rx2_retinrisk_10 = (1-rx2_heidelta*delta_a1c*hr_retin)*retinrisk_10
rx2_retinrisk_life = (1-rx2_heidelta*delta_a1c*hr_retin)*retinrisk_life
rx2_neurorisk_10 = (1-rx2_heidelta*delta_a1c*hr_neuro)*neurorisk_10
rx2_neurorisk_life = (1-rx2_heidelta*delta_a1c*hr_neuro)* neurorisk_life
rx2_allmort_10 = (1-rx2_heidelta*hr_allmort)*mortrisk_10
rx2_allmort_life = (1-rx2_heidelta*hr_allmort)*mortrisk_life
  
```


## translate into QALYs, 10year and lifetime
```{r QALYS lost at baseline}

set.seed(7)
ascvd_events_10 = rbinom(iters, 1, ascvd_10)
set.seed(8)
ascvd_events_life = rbinom(iters, 1, ascvd_life)
set.seed(9)
dminc_events_10 = rbinom(iters, 1, dminc_10)*(dm==0)
set.seed(10)
dminc_events_life = rbinom(iters, 1, dminc_life)*(dm==0)
set.seed(11)
dminter_10 = rbinom(iters,1,1-exp(-dminc_rate*10/2))
set.seed(12)
dminter_life = rbinom(iters,1,1-exp(-dminc_rate*lifeexp/2))
set.seed(13)
esrd_events_10 = rbinom(iters, 1, esrdrisk_10)*(dm==1 | dminter_10==1)
set.seed(14)
esrd_events_life = rbinom(iters, 1, esrdrisk_life)*(dm==1 | dminter_life==1)
set.seed(15)
retin_events_10 = rbinom(iters, 1, retinrisk_10)*(dm==1 | dminter_10==1)
set.seed(16)
retin_events_life = rbinom(iters, 1, retinrisk_life)*(dm==1 | dminter_life==1)
set.seed(17)
neuro_events_10 = rbinom(iters, 1, neurorisk_10)*(dm==1 | dminter_10==1)
set.seed(18)
neuro_events_life = rbinom(iters, 1, neurorisk_life)*(dm==1 | dminter_life==1)
set.seed(19)
mort_events_10 = rbinom(iters, 1, mortrisk_10)
set.seed(20)
mort_events_life = rbinom(iters, 1, mortrisk_life)

# Salomon et al., Lancet 2012; 380: 2129–43
# Disease event,	Estimated disutility on scale of 0 to 1 (95% CI)
# Atherosclerotic cardiovascular disease	0.28 (0.06, 0.57)
# DM incident, uncomplicated 0.01 (0, 0.02)
# Renal failure/end-stage renal disease	0.57 (0.40, 0.75)
# Retinopathy	0.20 (0.10, 0.40)
# Neuropathy	0.10 (0.05, 0.20)

set.seed(21)
d_ascvd = rnorm(iters,.28,(.28-.06)/1.96)
d_ascvd[d_ascvd<0]=0
d_dminc = rnorm(iters,.01,.01/1.96)
d_dminc[d_dminc<0]=0
d_esrd = rnorm(iters,.57,(.57-.4)/1.96)
d_esrd[d_esrd<0]=0
d_retin = rnorm(iters,.2,(.2-.1)/1.96)
d_retin[d_retin<0]=0
d_neuro = rnorm(iters,.1,(.1-.05)/1.96)
d_neuro[d_neuro<0]=0

# QALYS lost
q_ascvd_10 = d_ascvd*10/2*ascvd_events_10*(mort_events_10==0)+
  1*10/2*ascvd_events_10*(mort_events_10==1)
q_ascvd_life = d_ascvd*lifeexp/2*ascvd_events_life*(mort_events_life==0)+
  1*lifeexp/2*ascvd_events_life*(mort_events_life==1)
q_dminc_10 = d_dminc*10/2*dminc_events_10*(mort_events_10==0)+
  1*10/2*dminc_events_10*(mort_events_10==1)
q_dminc_life = d_dminc*lifeexp/2*dminc_events_life*(mort_events_life==0)+
  1*lifeexp/2*dminc_events_life*(mort_events_life==1)
q_esrd_10 = d_esrd*10/2*esrd_events_10*(mort_events_10==0)+
  1*10/2*esrd_events_10*(mort_events_10==1)
q_esrd_life = d_esrd*lifeexp/2*esrd_events_life*(mort_events_life==0)+
  1*lifeexp/2*esrd_events_life*(mort_events_life==1)
q_retin_10 = d_retin*10/2*retin_events_10*(mort_events_10==0)+
  1*10/2*retin_events_10*(mort_events_10==1)
q_retin_life = d_retin*lifeexp/2*retin_events_life*(mort_events_life==0)+
  1*lifeexp/2*retin_events_life*(mort_events_life==1)
q_neuro_10 = d_neuro*10/2*neuro_events_10*(mort_events_10==0)+
  1*10/2*neuro_events_10*(mort_events_10==1)
q_neuro_life = d_neuro*lifeexp/2*neuro_events_life*(mort_events_life==0)+
  1*lifeexp/2*neuro_events_life*(mort_events_life==1)
q_allmort_10 = 10/2*(ascvd_events_10==0)*(dminc_events_10==0)*(esrd_events_10==0)*(retin_events_10==0)*(neuro_events_10==0)*(mort_events_10==1)
q_allmort_life = lifeexp/2*(ascvd_events_life==0)*(dminc_events_life==0)*(esrd_events_life==0)*(retin_events_life==0)*(neuro_events_life==0)*(mort_events_life==1)

library(data.table)
qalys_10 = data.table(q_ascvd_10, q_dminc_10, q_esrd_10, q_retin_10, q_neuro_10, q_allmort_10)
qalys_life = data.table(q_ascvd_life, q_dminc_life, q_esrd_life, q_retin_life, q_neuro_life, q_allmort_life)


# QALYS lost under treatment 1

set.seed(7)
rx1_ascvd_events_10 = rbinom(iters, 1, rx1_ascvd_10)
set.seed(8)
rx1_ascvd_events_life = rbinom(iters, 1, rx1_ascvd_life)
set.seed(9)
rx1_dminc_events_10 = rbinom(iters, 1, rx1_dminc_10)*(dm==0)
set.seed(10)
rx1_dminc_events_life = rbinom(iters, 1, rx1_dminc_life)*(dm==0)
set.seed(11)
rx1_dminter_10 = rbinom(iters,1,1-exp(log(1-rx1_dminc_10)/10*10/2))
set.seed(12)
rx1_dminter_life = rbinom(iters,1,1-exp(log(1-rx1_dminc_life)/10*lifeexp/2))
set.seed(13)
rx1_esrd_events_10 = rbinom(iters, 1, rx1_esrdrisk_10)*(dm==1 | rx1_dminter_10==1)
set.seed(14)
rx1_esrd_events_life = rbinom(iters, 1, rx1_esrdrisk_life)*(dm==1 | rx1_dminter_life==1)
set.seed(15)
rx1_retin_events_10 = rbinom(iters, 1, rx1_retinrisk_10)*(dm==1 | rx1_dminter_10==1)
set.seed(16)
rx1_retin_events_life = rbinom(iters, 1, rx1_retinrisk_life)*(dm==1 | rx1_dminter_life==1)
set.seed(17)
rx1_neuro_events_10 = rbinom(iters, 1, rx1_neurorisk_10)*(dm==1 | rx1_dminter_10==1)
set.seed(18)
rx1_neuro_events_life = rbinom(iters, 1, rx1_neurorisk_life)*(dm==1 | rx1_dminter_life==1)
set.seed(19)
rx1_mort_events_10 = rbinom(iters, 1, rx1_allmort_10)
set.seed(20)
rx1_mort_events_life = rbinom(iters, 1, rx1_allmort_life)


# QALYS lost
rx1_q_ascvd_10 = d_ascvd*10/2*rx1_ascvd_events_10*(rx1_mort_events_10==0)+
  1*10/2*rx1_ascvd_events_10*(rx1_mort_events_10==1)
rx1_q_ascvd_life = d_ascvd*lifeexp/2*rx1_ascvd_events_life*(rx1_mort_events_life==0)+
  1*lifeexp/2*rx1_ascvd_events_life*(rx1_mort_events_life==1)
rx1_q_dminc_10 = d_dminc*10/2*rx1_dminc_events_10*(rx1_mort_events_10==0)+
  1*10/2*rx1_dminc_events_10*(rx1_mort_events_10==1)
rx1_q_dminc_life = d_dminc*lifeexp/2*rx1_dminc_events_life*(rx1_mort_events_life==0)+
  1*lifeexp/2*rx1_dminc_events_life*(rx1_mort_events_life==1)
rx1_q_esrd_10 = d_esrd*10/2*rx1_esrd_events_10*(rx1_mort_events_10==0)+
  1*10/2*rx1_esrd_events_10*(rx1_mort_events_10==1)
rx1_q_esrd_life = d_esrd*lifeexp/2*rx1_esrd_events_life*(rx1_mort_events_life==0)+
  1*lifeexp/2*rx1_esrd_events_life*(rx1_mort_events_life==1)
rx1_q_retin_10 = d_retin*10/2*rx1_retin_events_10*(rx1_mort_events_10==0)+
  1*10/2*rx1_retin_events_10*(rx1_mort_events_10==1)
rx1_q_retin_life = d_retin*lifeexp/2*rx1_retin_events_life*(rx1_mort_events_life==0)+
  1*lifeexp/2*rx1_retin_events_life*(rx1_mort_events_life==1)
rx1_q_neuro_10 = d_neuro*10/2*rx1_neuro_events_10*(rx1_mort_events_10==0)+
  1*10/2*rx1_neuro_events_10*(rx1_mort_events_10==1)
rx1_q_neuro_life = d_neuro*lifeexp/2*rx1_neuro_events_life*(rx1_mort_events_life==0)+
  1*lifeexp/2*rx1_neuro_events_life*(rx1_mort_events_life==1)
rx1_q_allmort_10 = 10/2*(rx1_ascvd_events_10==0)*(rx1_dminc_events_10==0)*(rx1_esrd_events_10==0)*(rx1_retin_events_10==0)*(rx1_neuro_events_10==0)*(rx1_mort_events_10==1)
rx1_q_allmort_life = lifeexp/2*(rx1_ascvd_events_life==0)*(rx1_dminc_events_life==0)*(rx1_esrd_events_life==0)*(rx1_retin_events_life==0)*(rx1_neuro_events_life==0)*(rx1_mort_events_life==1)

rx1_qalys_10 = data.table(rx1_q_ascvd_10, rx1_q_dminc_10, rx1_q_esrd_10, rx1_q_retin_10, rx1_q_neuro_10, rx1_q_allmort_10)
rx1_qalys_life = data.table(rx1_q_ascvd_life, rx1_q_dminc_life, rx1_q_esrd_life, rx1_q_retin_life, rx1_q_neuro_life, rx1_q_allmort_life)



# QALYS lost under treatment 2

set.seed(7)
rx2_ascvd_events_10 = rbinom(iters, 1, rx2_ascvd_10)
set.seed(8)
rx2_ascvd_events_life = rbinom(iters, 1, rx2_ascvd_life)
set.seed(9)
rx2_dminc_events_10 = rbinom(iters, 1, rx2_dminc_10)*(dm==0)
set.seed(10)
rx2_dminc_events_life = rbinom(iters, 1, rx2_dminc_life)*(dm==0)
set.seed(11)
rx2_dminter_10 = rbinom(iters,1,1-exp(log(1-rx2_dminc_10)/10*10/2))
set.seed(12)
rx2_dminter_life = rbinom(iters,1,1-exp(log(1-rx2_dminc_life)/10*lifeexp/2))
set.seed(13)
rx2_esrd_events_10 = rbinom(iters, 1, rx2_esrdrisk_10)*(dm==1 | rx2_dminter_10==1)
set.seed(14)
rx2_esrd_events_life = rbinom(iters, 1, rx2_esrdrisk_life)*(dm==1 | rx2_dminter_life==1)
set.seed(15)
rx2_retin_events_10 = rbinom(iters, 1, rx2_retinrisk_10)*(dm==1 | rx2_dminter_10==1)
set.seed(16)
rx2_retin_events_life = rbinom(iters, 1, rx2_retinrisk_life)*(dm==1 | rx2_dminter_life==1)
set.seed(17)
rx2_neuro_events_10 = rbinom(iters, 1, rx2_neurorisk_10)*(dm==1 | rx2_dminter_10==1)
set.seed(18)
rx2_neuro_events_life = rbinom(iters, 1, rx2_neurorisk_life)*(dm==1 | rx2_dminter_life==1)
set.seed(19)
rx2_mort_events_10 = rbinom(iters, 1, rx2_allmort_10)
set.seed(20)
rx2_mort_events_life = rbinom(iters, 1, rx2_allmort_life)


# QALYS lost
rx2_q_ascvd_10 = d_ascvd*10/2*rx2_ascvd_events_10*(rx2_mort_events_10==0)+
  1*10/2*rx2_ascvd_events_10*(rx2_mort_events_10==1)
rx2_q_ascvd_life = d_ascvd*lifeexp/2*rx2_ascvd_events_life*(rx2_mort_events_life==0)+
  1*lifeexp/2*rx2_ascvd_events_life*(rx2_mort_events_life==1)
rx2_q_dminc_10 = d_dminc*10/2*rx2_dminc_events_10*(rx2_mort_events_10==0)+
  1*10/2*rx2_dminc_events_10*(rx2_mort_events_10==1)
rx2_q_dminc_life = d_dminc*lifeexp/2*rx2_dminc_events_life*(rx2_mort_events_life==0)+
  1*lifeexp/2*rx2_dminc_events_life*(rx2_mort_events_life==1)
rx2_q_esrd_10 = d_esrd*10/2*rx2_esrd_events_10*(rx2_mort_events_10==0)+
  1*10/2*rx2_esrd_events_10*(rx2_mort_events_10==1)
rx2_q_esrd_life = d_esrd*lifeexp/2*rx2_esrd_events_life*(rx2_mort_events_life==0)+
  1*lifeexp/2*rx2_esrd_events_life*(rx2_mort_events_life==1)
rx2_q_retin_10 = d_retin*10/2*rx2_retin_events_10*(rx2_mort_events_10==0)+
  1*10/2*rx2_retin_events_10*(rx2_mort_events_10==1)
rx2_q_retin_life = d_retin*lifeexp/2*rx2_retin_events_life*(rx2_mort_events_life==0)+
  1*lifeexp/2*rx2_retin_events_life*(rx2_mort_events_life==1)
rx2_q_neuro_10 = d_neuro*10/2*rx2_neuro_events_10*(rx2_mort_events_10==0)+
  1*10/2*rx2_neuro_events_10*(rx2_mort_events_10==1)
rx2_q_neuro_life = d_neuro*lifeexp/2*rx2_neuro_events_life*(rx2_mort_events_life==0)+
  1*lifeexp/2*rx2_neuro_events_life*(rx2_mort_events_life==1)
rx2_q_allmort_10 = 10/2*(rx2_ascvd_events_10==0)*(rx2_dminc_events_10==0)*(rx2_esrd_events_10==0)*(rx2_retin_events_10==0)*(rx2_neuro_events_10==0)*(rx2_mort_events_10==1)
rx2_q_allmort_life = lifeexp/2*(rx2_ascvd_events_life==0)*(rx2_dminc_events_life==0)*(rx2_esrd_events_life==0)*(rx2_retin_events_life==0)*(rx2_neuro_events_life==0)*(rx2_mort_events_life==1)

rx2_qalys_10 = data.table(rx2_q_ascvd_10, rx2_q_dminc_10, rx2_q_esrd_10, rx2_q_retin_10, rx2_q_neuro_10, rx2_q_allmort_10)
rx2_qalys_life = data.table(rx2_q_ascvd_life, rx2_q_dminc_life, rx2_q_esrd_life, rx2_q_retin_life, rx2_q_neuro_life, rx2_q_allmort_life)
```


## calculate costs, healthcare and societal perspective [where latter includes productivity and agriculture econ effects]
``` {r costs}
# total annual healthcare cost estimates from Optum Clinformatics
# $61,614 for each cardiovascular event (95% CI: $61,095, $62,132)
# $22,526 for each incident uncomplicated case of diabetes (95% CI: $21,919, $23,132)
# $293,490 for each case of end-stage renal disease (95% CI: $290,584, $296,396)
# $26,174 for each case of retinopathy (95% CI: $25,578, $26,769)
# $48,432 for each case of neuropathy (95% CI: $46,470, $50,393)

set.seed(21)
c_ascvd = rnorm(iters,61614,(61614-61095)/1.96)
c_ascvd[c_ascvd<0]=0
set.seed(22)
c_dminc = rnorm(iters,22526,(22526-21919)/1.96)
c_dminc[c_dminc<0]=0
set.seed(23)
c_esrd = rnorm(iters,293490,(293490-290584)/1.96)
c_esrd[c_esrd<0]=0
set.seed(24)
c_retin = rnorm(iters,26174,(26174-25578)/1.96)
c_retin[c_retin<0]=0
set.seed(25)
c_neuro = rnorm(iters,48432,(48432-46470)/1.96)
c_neuro[c_neuro<0]=0


# healthcare costs at baseline
c_ascvd_10 = c_ascvd*10/2*ascvd_events_10
c_ascvd_life = c_ascvd*lifeexp/2*ascvd_events_life
c_dminc_10 = c_dminc*10/2*dminc_events_10
c_dminc_life = c_dminc*lifeexp/2*dminc_events_life
c_esrd_10 = c_esrd*10/2*esrd_events_10
c_esrd_life = c_esrd*lifeexp/2*esrd_events_life
c_retin_10 = c_retin*10/2*retin_events_10
c_retin_life = c_retin*lifeexp/2*retin_events_life
c_neuro_10 = c_neuro*10/2*neuro_events_10
c_neuro_life = c_neuro*lifeexp/2*neuro_events_life

costs_10 = data.table(c_ascvd_10, c_dminc_10, c_esrd_10, c_retin_10, c_neuro_10)
costs_life = data.table(c_ascvd_life, c_dminc_life, c_esrd_life, c_retin_life, c_neuro_life)

# healthcare costs under rx 1
rx1_c_ascvd_10 = c_ascvd*10/2*rx1_ascvd_events_10
rx1_c_ascvd_life = c_ascvd*lifeexp/2*rx1_ascvd_events_life
rx1_c_dminc_10 = c_dminc*10/2*rx1_dminc_events_10
rx1_c_dminc_life = c_dminc*lifeexp/2*rx1_dminc_events_life
rx1_c_esrd_10 = c_esrd*10/2*rx1_esrd_events_10
rx1_c_esrd_life = c_esrd*lifeexp/2*rx1_esrd_events_life
rx1_c_retin_10 = c_retin*10/2*rx1_retin_events_10
rx1_c_retin_life = c_retin*lifeexp/2*rx1_retin_events_life
rx1_c_neuro_10 = c_neuro*10/2*rx1_neuro_events_10
rx1_c_neuro_life = c_neuro*lifeexp/2*rx1_neuro_events_life

rx1_costs_10 = data.table(rx1_c_ascvd_10, rx1_c_dminc_10, rx1_c_esrd_10, rx1_c_retin_10, rx1_c_neuro_10)
rx1_costs_life = data.table(rx1_c_ascvd_life, rx1_c_dminc_life, rx1_c_esrd_life, rx1_c_retin_life, rx1_c_neuro_life)

# healthcare costs under rx 2
rx2_c_ascvd_10 = c_ascvd*10/2*rx2_ascvd_events_10
rx2_c_ascvd_life = c_ascvd*lifeexp/2*rx2_ascvd_events_life
rx2_c_dminc_10 = c_dminc*10/2*rx2_dminc_events_10
rx2_c_dminc_life = c_dminc*lifeexp/2*rx2_dminc_events_life
rx2_c_esrd_10 = c_esrd*10/2*rx2_esrd_events_10
rx2_c_esrd_life = c_esrd*lifeexp/2*rx2_esrd_events_life
rx2_c_retin_10 = c_retin*10/2*rx2_retin_events_10
rx2_c_retin_life = c_retin*lifeexp/2*rx2_retin_events_life
rx2_c_neuro_10 = c_neuro*10/2*rx2_neuro_events_10
rx2_c_neuro_life = c_neuro*lifeexp/2*rx2_neuro_events_life

rx2_costs_10 = data.table(rx2_c_ascvd_10, rx2_c_dminc_10, rx2_c_esrd_10, rx2_c_retin_10, rx2_c_neuro_10)
rx2_costs_life = data.table(rx2_c_ascvd_life, rx2_c_dminc_life, rx2_c_esrd_life, rx2_c_retin_life, rx2_c_neuro_life)




# productivity cost estimates
# $1,085 for each cardiovascular disease event (95% CI: $521, $1,649).
# $5,811 for each complication of diabetes (95% CI: $2,571, $9,052) 
# 1 	Song X, Quek RGW, Gandra SR, Cappell KA, Fowler R, Cong Z. Productivity loss and indirect costs associated with cardiovascular events and related clinical procedures. BMC Health Serv Res. 2015;15:245. doi:10.1186/s12913-015-0925-x
# 2. 	Ng YC, Jacobs P, Johnson JA. Productivity losses associated with diabetes in the US. Diabetes Care. 2001;24(2):257-261. doi:10.2337/DIACARE.24.2.257

set.seed(21)
p_ascvd = rnorm(iters,1085,(1085-521)/1.96)
p_ascvd[p_ascvd<0]=0
p_dminc = 0
set.seed(23)
p_esrd = rnorm(iters,5811,(5811-2571)/1.96)
p_esrd[p_esrd<0]=0
p_retin = p_esrd
p_neuro = p_esrd


# productivity costs at baseline
p_ascvd_10 = p_ascvd*10/2*ascvd_events_10
p_ascvd_life = p_ascvd*lifeexp/2*ascvd_events_life
p_dminp_10 = p_dminc*10/2*dminp_events_10
p_dminp_life = p_dminc*lifeexp/2*dminp_events_life
p_esrd_10 = p_esrd*10/2*esrd_events_10
p_esrd_life = p_esrd*lifeexp/2*esrd_events_life
p_retin_10 = p_retin*10/2*retin_events_10
p_retin_life = p_retin*lifeexp/2*retin_events_life
p_neuro_10 = p_neuro*10/2*neuro_events_10
p_neuro_life = p_neuro*lifeexp/2*neuro_events_life

prod_10 = data.table(p_ascvd_10, p_dminp_10, p_esrd_10, p_retin_10, p_neuro_10)
prod_life = data.table(p_ascvd_life, p_dminp_life, p_esrd_life, p_retin_life, p_neuro_life)

# productivity costs under rx 1
rx1_p_ascvd_10 = p_ascvd*10/2*rx1_ascvd_events_10
rx1_p_ascvd_life = p_ascvd*lifeexp/2*rx1_ascvd_events_life
rx1_p_dminp_10 = p_dminc*10/2*rx1_dminp_events_10
rx1_p_dminp_life = p_dminc*lifeexp/2*rx1_dminp_events_life
rx1_p_esrd_10 = p_esrd*10/2*rx1_esrd_events_10
rx1_p_esrd_life = p_esrd*lifeexp/2*rx1_esrd_events_life
rx1_p_retin_10 = p_retin*10/2*rx1_retin_events_10
rx1_p_retin_life = p_retin*lifeexp/2*rx1_retin_events_life
rx1_p_neuro_10 = p_neuro*10/2*rx1_neuro_events_10
rx1_p_neuro_life = p_neuro*lifeexp/2*rx1_neuro_events_life

rx1_prod_10 = data.table(rx1_p_ascvd_10, rx1_p_dminp_10, rx1_p_esrd_10, rx1_p_retin_10, rx1_p_neuro_10)
rx1_prod_life = data.table(rx1_p_ascvd_life, rx1_p_dminp_life, rx1_p_esrd_life, rx1_p_retin_life, rx1_p_neuro_life)

# productivity costs under rx 2
rx2_p_ascvd_10 = p_ascvd*10/2*rx2_ascvd_events_10
rx2_p_ascvd_life = p_ascvd*lifeexp/2*rx2_ascvd_events_life
rx2_p_dminp_10 = p_dminc*10/2*rx2_dminp_events_10
rx2_p_dminp_life = p_dminc*lifeexp/2*rx2_dminp_events_life
rx2_p_esrd_10 = p_esrd*10/2*rx2_esrd_events_10
rx2_p_esrd_life = p_esrd*lifeexp/2*rx2_esrd_events_life
rx2_p_retin_10 = p_retin*10/2*rx2_retin_events_10
rx2_p_retin_life = p_retin*lifeexp/2*rx2_retin_events_life
rx2_p_neuro_10 = p_neuro*10/2*rx2_neuro_events_10
rx2_p_neuro_life = p_neuro*lifeexp/2*rx2_neuro_events_life

rx2_prod_10 = data.table(rx2_p_ascvd_10, rx2_p_dminp_10, rx2_p_esrd_10, rx2_p_retin_10, rx2_p_neuro_10)
rx2_prod_life = data.table(rx2_p_ascvd_life, rx2_p_dminp_life, rx2_p_esrd_life, rx2_p_retin_life, rx2_p_neuro_life)




# intervention costs, with placeholder 15% overhead cost
rx1_intcosts_10 = 300*10*iters*1.15
rx1_intcosts_life = 300*lifeexp*iters*1.15

rx2_intcosts_10 = 300*10*iters*1.15
rx2_intcosts_life = 300*lifeexp*iters*1.15

# economic benefits from intervention, placeholder $50 per person per year net increase benefit to farms
rx1_econben_10 =50*10*iters
rx1_econben_life =50*lifeexp*iters

rx2_econben_10 =50*10*iters
rx2_econben_life =50*lifeexp*iters


```


# results tables, healthcare perspective, 10yr and lifetime horizon
``` {r results tables, healthcare perspective only}

# healthcare costs lost at baseline
colSums(costs_10)/iters*10000
sum(colSums(costs_10)/iters*10000)
colSums(costs_life)/iters*10000
sum(colSums(costs_life)/iters*10000)

# healthcare costs lost under Rx 1
colSums(rx1_costs_10)/iters*10000
sum(colSums(rx1_costs_10)/iters*10000)
sum(rx1_intcosts_10)
colSums(rx1_costs_life)/iters*10000
sum(colSums(rx1_costs_life)/iters*10000)
sum(rx1_intcosts_life)

# healthcare costs lost under Rx 2
colSums(rx2_costs_10)/iters*10000
sum(colSums(rx2_costs_10)/iters*10000)
sum(rx2_intcosts_10)
colSums(rx2_costs_life)/iters*10000
sum(colSums(rx2_costs_life)/iters*10000)
sum(rx2_intcosts_life)

# QALYS lost at baseline
colSums(qalys_10)/iters*10000
sum(colSums(qalys_10)/iters*10000)
colSums(qalys_life)/iters*10000
sum(colSums(qalys_life)/iters*10000)

# QALYS lost under Rx 1
colSums(rx1_qalys_10)/iters*10000
sum(colSums(rx1_qalys_10)/iters*10000)
colSums(rx1_qalys_life)/iters*10000
sum(colSums(rx1_qalys_life)/iters*10000)

# QALYS lost under Rx 2
colSums(rx2_qalys_10)/iters*10000
sum(colSums(rx2_qalys_10)/iters*10000)
colSums(rx2_qalys_life)/iters*10000
sum(colSums(rx2_qalys_life)/iters*10000)


# ICER of Rx 1 healthcare
(sum(colSums(rx1_costs_10+rx1_intcosts_10)/iters*10000)-sum(colSums(costs_10)/iters*10000))/
  (sum(colSums(rx1_qalys_10)/iters*10000)-sum(colSums(qalys_10)/iters*10000))
(sum(colSums(rx1_costs_life+rx1_intcosts_life)/iters*10000)-sum(colSums(costs_life)/iters*10000))/
  (sum(colSums(rx1_qalys_life)/iters*10000)-sum(colSums(qalys_life)/iters*10000))

# ICER of Rx 2 healthcare
(sum(colSums(rx2_costs_10+rx2_intcosts_10)/iters*10000)-sum(colSums(costs_10)/iters*10000))/
  (sum(colSums(rx2_qalys_10)/iters*10000)-sum(colSums(qalys_10)/iters*10000))
(sum(colSums(rx2_costs_life+rx2_intcosts_life)/iters*10000)-sum(colSums(costs_life)/iters*10000))/
  (sum(colSums(rx2_qalys_life)/iters*10000)-sum(colSums(qalys_life)/iters*10000))

```


# results tables, societal perspective, 10yr and lifetime horizon
``` {r results tables, societal perspective}

#  prod costs lost at baseline
colSums(prod_10)/iters*10000
sum(colSums(prod_10)/iters*10000)
colSums(prod_life)/iters*10000
sum(colSums(prod_life)/iters*10000)

#  prod costs lost under Rx 1
colSums(rx1_prod_10)/iters*10000
sum(colSums(rx1_prod_10)/iters*10000)
colSums(rx1_prod_life)/iters*10000
sum(colSums(rx1_prod_life)/iters*10000)

#  prod costs lost under Rx 2
colSums(rx2_prod_10)/iters*10000
sum(colSums(rx2_prod_10)/iters*10000)
colSums(rx2_prod_life)/iters*10000
sum(colSums(rx2_prod_life)/iters*10000)

# econ gains under Rx 1
sum(colSums(rx1_econben_10)/iters*10000)
sum(colSums(rx1_econben_life)/iters*10000)

# econ gains under Rx 2
sum(colSums(rx2_econben_10)/iters*10000)
sum(colSums(rx2_econben_life)/iters*10000)


# ICER of Rx 1 societal
(sum(colSums(rx1_costs_10+rx1_intcosts_10+rx1_prod_10-rx1_econben_10)/iters*10000)-sum(colSums(costs_10+prod_10)/iters*10000))/(sum(colSums(rx1_qalys_10)/iters*10000)-sum(colSums(qalys_10)/iters*10000))
(sum(colSums(rx1_costs_life+rx1_intcosts_life+rx1_prod_life-rx1_econben_life)/iters*10000)-sum(colSums(costs_life+prod_life)/iters*10000))/(sum(colSums(rx1_qalys_life)/iters*10000)-sum(colSums(qalys_life)/iters*10000))

# ICER of Rx 2 societal
(sum(colSums(rx2_costs_10+rx2_intcosts_10+rx2_prod_10-rx2_econben_10)/iters*10000)-sum(colSums(costs_10+prod_10)/iters*10000))/(sum(colSums(rx2_qalys_10)/iters*10000)-sum(colSums(qalys_10)/iters*10000))
(sum(colSums(rx2_costs_life+rx2_intcosts_life+rx2_prod_life-rx2_econben_life)/iters*10000)-sum(colSums(costs_life+prod_life)/iters*10000))/(sum(colSums(rx2_qalys_life)/iters*10000)-sum(colSums(qalys_life)/iters*10000))

```

## sensitivity analysis to see what overhead rate represents the 'break-even' between cash and CSA (i.e. how cheap does the CSA have to run to offset the extra overhead) (or alternatively how much bigger an effect size would it need over cash, taking additional overhead as fixed).

